%%%%%%%%%%%%%%%%%%%%%%%%HEADER%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,oneside,12pt]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}
\usepackage{amssymb}
\usepackage{varioref}
\usepackage[margin=.9in]{geometry}
\usepackage{url}
\usepackage{color}   	%May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
	colorlinks=true, 	%set true if you want colored links
	linktoc=all,     	%set to all if you want both sections and subsections linked
	linkcolor=blue,  	%choose some color if you want links to stand out
}
\usepackage{marvosym}	%for emoticons
\usepackage{tikz}		%for folder tree


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{\huge \bf MCA Website - SysAd Manual}
\author{\normalsize Ashfaque Ahammed \texttt{<getashfa@gmail.com>}}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents
%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
	This document describes the overall picture of MCA website. 
	
	\subsection{Brief History}
	\paragraph{}MCA holds a huge collection of Malayalam movies for many years. They had stood up a \texttt{ftp} server and everything was fine. One day I was searching for an old Mohanlal-movie(thouugh I'm not a fan \Smiley{}), I couldn't find it out, even it was actually there. Yes, it was not that well organized. So the \Lightning idea come from the fact that to bring something better to navigate(of-course movies). I was just a newbie to web-development other that those simple \texttt{html} only pages made on school days. I started coding this project back in 2015 January and it took me more than two months to reach a point that it can be launched, as I was doing it on my free time. MCA council gave me all the support on this especially \textit{Sharan, Ashwin, Ramzan, Jayasankar}. Website initially launched on March 15, 20015 while people and library tabs left to code.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Website Directory Structure}
	\usetikzlibrary{trees}
	\tikzstyle{every node}=[draw=black,thick,anchor=west]
	\tikzstyle{selected}=[draw=red,fill=red!30]
	\tikzstyle{optional}=[dashed,fill=gray!50]
	\begin{tikzpicture}[%
	grow via three points={one child at (0.5,-0.7) and
		two children at (0.5,-0.7) and (0.5,-1.4)},
	edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
	\node {texmf}
	child { node {doc}}		
	child { node {fonts}}
	child { node {source}}
	child { node [selected] {tex}
		child { node {generic}}
		child { node [optional] {latex}}
		child { node {plain}}
	}
	child [missing] {}				
	child [missing] {}				
	child [missing] {}				
	child { node {texdoc}};
	\end{tikzpicture}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}